Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
add comments to sec 4- need to be rivised

Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
hierarchical clustering is robust against noise.
In agglomerative clustering, weights of
parallel edges are merged into single edges.
For image segmentation, the length
weighted mean is used to do this update.

We propose to use Energy Based Hierarchical Clustering (EHC) to find
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
To make EHC follow the energy, we propose 
the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

>>>>

Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
{\color{red} hierarchical clustering is robust against noise}.
{\color{yellow} [ First most similar nodes are merged...]
In agglomerative clustering, weights of
parallel edges are merged into single edges.}
For image segmentation, the length
weighted mean is used to do this update [ref].

[We contrary on those works work directly on energy functions and that why ...]
We propose to use Energy Based Hierarchical Clustering (EHC) to find
solutions for correlation clustering.

\textit{move this up} [ In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
]

To make EHC follow the energy, we propose 
the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.
